Initial spatial conditions in simulation models: the missing leg of sensitivity analyses?

### 2017-07-05 paper.tex
Update on Overleaf.

\author{Juste Raimbault\affilnum{1,4}, 
Cl{\' e}mentine Cottineau\affilnum{2},
Marion Le Texier\affilnum{3}, 
Florent Le N{\' e}chet\affilnum{4}, 
Romain Reuillon\affilnum{1,5}
}

\affiliation{\affilnum{1}UMR 8504 G{\'e}ographie-cit{\'e}s, Paris, France\\
\affilnum{2}Centre for Advanced Spatial Analysis, University College London, UK\\
\affilnum{3}UMR 6266 IDEES, Universit{\'e} de Rouen Normandie, France\\
\affilnum{4}Laboratoire Ville Mobilit{\'e} Transport, Universit{\'e} Paris-Est, France\\
\affilnum{5}Institut des Syst{\`e}mes Complexes Paris Ile-de-France, France}

>>>>

\author{Juste Raimbault\affilnum{1,2}, 
Cl{\' e}mentine Cottineau\affilnum{3},
Marion Le Texier\affilnum{4}, 
Florent Le N{\' e}chet\affilnum{2}, 
Romain Reuillon\affilnum{1,5}
}

\affiliation{\affilnum{1}UMR 8504 G{\'e}ographie-cit{\'e}s, Paris, France\\
\affilnum{2}Laboratoire Ville Mobilit{\'e} Transport, Universit{\'e} Paris-Est, France\\
\affilnum{3}Centre for Advanced Spatial Analysis, University College London, UK\\
\affilnum{4}UMR 6266 IDEES, Universit{\'e} de Rouen Normandie, France\\
\affilnum{5}Institut des Syst{\`e}mes Complexes Paris Ile-de-France, France}
